Metabric

### 2023-02-08 analyses/metabricStudy.Rmd
checkpoint

---
title: "Metabric"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.1
---

@@

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_metabric<-T
pycox<-reticulate::import("pycox")
source_python('src/getMetabricData.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 0
epo=as.numeric(params$epo)
patience = as.numeric(params$patience)
iteration=as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)

@@

metabric<-getMetabric()
colnames(metabric)[ncol(metabric)-1]<-'time'
colnames(metabric)[ncol(metabric)]<-'status'
data<-as.data.frame(model.matrix(~.,metabric)[,-1])
data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

@@

@@

  ##########################
  ###DSM
  ##########################
  source_python('src/dsmScript.py')
  dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,val=val,times=times,tPos=ncol(train)-2,ePos=ncol(train)-1)
  if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){

@@

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # 
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
    source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)
  # source_python('src/deephitter.py')
  # hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  # hitnnSurv<-t(hitnnSurv)
  # colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  # deephitCleaned<-pyProcess(hitnnSurv,times=times)
  # colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  # py_run_string("del fitDeephit")
  # rm(fitDeephit)
  # 
  ############################
  ###PMNNsplines
  ############################  
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'tanh')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = 0.0001)
  )

>>>>

---
title: "Metabric"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 1
  layer1: 100
  layer2: 100
  layer3: 50
  layer4: 50
  drpt: 0.1
  lr: 0.001
---

@@

```{r setup, include=T}
set.seed(2)#set seed to 2, because testing set had shortest survival time censored, resulting in an error in the c-index calculation method.
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
eval_metabric<-T
pycox<-reticulate::import("pycox")
source_python('src/getMetabricData.py')
source_python("src/cIndex.py")
source_python("src/dsmScript.py")
source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
bsize=512
min_delta = 10^-7
epo=as.numeric(params$epo)
patience = as.numeric(params$patience)
iteration=as.numeric(params$iteration)
layer1<-as.numeric(params$layer1)
layer2<-as.numeric(params$layer2)
layer3<-as.numeric(params$layer3)
layer4<-as.numeric(params$layer4)
drpt<-as.numeric(params$drpt)
lr=as.numeric(params$lr)

@@

metabric<-getMetabric()
colnames(metabric)[ncol(metabric)-1]<-'time'
colnames(metabric)[ncol(metabric)]<-'status'
data<-as.data.frame(model.matrix(~.,metabric)[,-1])
#data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
covs<-colnames(data)

@@

  # times<-seq(from=min(test$time[fullTest$status==1]),
  #            to=max(test$time[fullTest$status==1]),
  #            length.out = 100
  # )

@@

  ##########################
  ###DSM
  ##########################
  source_python('src/dsmScript.py')
  dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo,val=val,times=times,tPos=ncol(train)-2,ePos=ncol(train)-1,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  if((sum(is.na(dsmSurv))==ncol(dsmSurv)*nrow(dsmSurv))){

@@

  coxnnsurv=fitDeepSurv(tiebreakTrain,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  coxnnsurv<-t(coxnnsurv)
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

  # coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
  #                 num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
  #                 early_stopping = TRUE, epochs = epo,
  #                 batch_size = bsize,device = "cpu",best_weights=T,
  #                 patience = patience,min_delta=min_delta,batch_norm = F,
  #                 learning_rate = 0.001,lr_decay=10^-7)
  # 
  # coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  # colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  # cnnCleaned<-pyProcess(coxnnsurv,times=times)
  # colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))
  ############################
  ###Deephit
  ############################  
    source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lay3=layer3,lay4=layer4,lr=lr)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)
  # source_python('src/deephitter.py')
  # hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  # hitnnSurv<-t(hitnnSurv)
  # colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  # deephitCleaned<-pyProcess(hitnnSurv,times=times)
  # colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  # py_run_string("del fitDeephit")
  # rm(fitDeephit)
  # 
  ############################
  ###PMNNsplines
  ############################  
    valcbtensor[[1]][[2]]<-rep(mod_cb_glm$offset[1],nrow(valcbtensor[[1]][[1]]))
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = lr)
  )

@@

  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  pmnn<-pmnnModel(features=colnames(mod_cb_glm$data)[-ncol(mod_cb_glm$data)],
                  feature_input = covars_input,
                  feature_output = covars_output,
                  originalData = mod_cb_glm$data,
                  offset=mod_cb_glm$offset,
                  timeVar = "time",
                  eventVar= "status",optimizer=optimizer_adam(learning_rate = lr)
  )
